Analysis for Project

### 2021-03-24 analysis/analysis.Rmd
caterpillar plot of estimates from model 4

>>>>

```{r}
coef_table <- tidy(model4) %>%
  filter(str_detect(term, "race") & str_detect(term, "/") & !str_detect(term, "Multiracial")) %>%
  mutate(term=str_remove(term, "race"))

ggplot(coef_table, aes(x=reorder(term, estimate, mean), y=estimate, 
                       ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error))+
  geom_hline(yintercept = 0, linetype=2)+
  geom_pointrange()+
  coord_flip()+
  theme_bw()
```
